% vim:ft=tex:
%
\documentclass{beamer}
\usetheme{Madrid}
\usepackage[latin1]{inputenc}
\usefonttheme{professionalfonts}
\usepackage{times}
\setbeamersize{text margin left=1em,text margin right=1em}
\setbeamertemplate{itemize items}[default]
\setbeamertemplate{enumerate items}[default]
\usepackage[utf8]{inputenc}

\title{Approximation Algorithms for Stochastic Inventory Control Models \\
    Levi, et. al
}
\author{Andrew Benton}
\date{\today}
\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}{Main Results}{}
    \begin{itemize}
    \item Studies problems with the following properties:
        \begin{itemize} 
            \item single item
            \item finite horizon
            \item correlated and nonstationary demand
        \end{itemize}
    \item Introduces ideas which allow MDP's to be avoided.
        \begin{itemize}
            \item \textit{Marginal Cost Accounting}
            \item \textit{Cost Balancing}
        \end{itemize}
    \item Guarantees constant worst-case performance policies for: 
        \begin{itemize}
            \item Periodic Review Stochastic Inventory Control Problem
            \item Stochastic Lot-Sizing Problem 
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{New Ideas Introduced}{Marginal Cost Accounting}
    \begin{itemize}
        \item Costs in the Markov Decision Process: 
            \begin{itemize}
                \item \textbf{Current Costs}: a function of current demand and current order.
                \item \textbf{Future Costs}: a function of future demand and future orders.
            \end{itemize}
        \item Costs in the Marginal Cost Accounting:
            \begin{itemize}
                \item \textbf{Current Costs}: a function of current demand and current order.
                \item \textbf{Future Costs}: a function of future demand.
            \end{itemize}
        \item The overall holding costs of ordered units over full horizon are due to the current decision.
        \item Once an order is made, those unit's holding costs are independent of any future decision.
    \end{itemize}
\end{frame}

\begin{frame}{New Ideas Introduced}{Cost Balancing}
    \begin{itemize}
        \item Any policy incurs costs due to overordering and underordering.
        \item An effective policy can balance these costs.
        \item Balancing leads to constant expected worst-case performance. 
    \end{itemize}
\end{frame}

\end{document}
